The unequal distribution of access to education and transport: insights from

### 2016-05-31 paper.Rmd
Update figures with captions

---
title: 'The unequal distribution of access to education and transport: insights from
  the São Paulo Metropolitan Region'
author: Ana I. Moreno-Monroy (Universitat Rovira i Virgili), Frederico R. Ramos (Fundação
  Getulio Vargas) and Robin Lovelace (University of Leeds)
output:
  word_document: default
  pdf_document:
    keep_tex: yes
  html_document:
    keep_md: yes
bibliography: school-access-bib.bib
---

@@

```{r inc-trans, echo=FALSE, out.width="80%"}
knitr::include_graphics("income_pc.png")
```

@@

#Data

@@

# Preliminary facts

@@

![Private secondary schools students home location](med_pr.png)
![Public secondary schools students home location](med_pu.png)

>>>>

---
title: 'The unequal distribution of access to education and transport: insights from
  the São Paulo Metropolitan Region'
author: Ana I. Moreno-Monroy (Universitat Rovira i Virgili), Frederico R. Ramos (Fundação
  Getulio Vargas) and Robin Lovelace (University of Leeds)
output:
  pdf_document:
    keep_tex: yes
  html_document:
    keep_md: yes
  word_document: default
bibliography: school-access-bib.bib
---

@@

```{r inc-trans, echo=FALSE, out.width="80%", fig.cap="Public transport system and income per capita in São Paulo, 2010."}
knitr::include_graphics("income_pc.png")
```

@@

# Data

@@

# Initial findings

@@

```{r, echo=FALSE, fig.cap="The home location of students attending public secondary schools students in São Paulo.", out.width="70%"}
knitr::include_graphics(c("med_pu.png"))
```

```{r, echo=FALSE, fig.cap="The home location of students attending private secondary schools students in São Paulo.", out.width="70%"}
knitr::include_graphics(c("med_pr.png"))
```

<!-- ![](med_pr.png) -->
<!-- ![Public secondary schools students home location](med_pu.png) -->
